---
title: "Indoor Location"
author: "Jonny, Tom, Jack"
date: "30 March 2015"
output: 
  beamer_presentation:
      fig_caption: true
---

## More Phone Problems

```{r, echo=FALSE, message=FALSE, warning=FALSE}
setwd("/Users/jonny/Documents/Study/locationcode/SpatialStatistics/")
source("TidyData.r")
source("EmpiricalKriging.R")
train = cleanData("Data/train.csv")
test = cleanData("Data/test.csv")
library(ggplot2)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Number of RSSI readings at each surveyed point, we can see lots of ones :(", fig.height=6}
plotData = train %>% filter(x >= 0 & x <= 10 & address %in% c("B1", "B2", "B4"))
plotData = plotData %>% group_by(x,y,address) %>% summarise(count = n())

ggplot(plotData, aes(x = x, y = y, label = count)) + 
  geom_text() + 
  facet_wrap(~address) +
  theme_bw() + ggtitle("Number of observations at each point")
```

## Trying to figure out what a certain paper means

Given a vector of $n$ RSSI readings, $\textbf{s} = (s_1, \dots, s_n)^T$, we want to calculate a position in $\mathbb{R}^2$, $\textbf{x} = (x,y)^T$. We use Bayes' rule:

$$ P(\textbf{x}|\textbf{s}) = \frac{P(\textbf{s}|\textbf{x})P(\textbf{x})}{\int P(\textbf{s}|\textbf{x}) P(\textbf{x}) d\textbf{x}}. $$

When calculating the MAP estimate using a Uniform prior for $P(\textbf{x})$, we can simplify Bayes' Rule:

$$ P(\textbf{x}|\textbf{s}) \propto P(\textbf{s}|\textbf{x}). $$

## Choosing the Likelihood Function

We must decide on a function for the likelihood, $P(\textbf{s}|\textbf{x}).$ The paper we read chose an exponential kernel:

\begin{equation}
\begin{aligned}
 P(\textbf{s}|\textbf{x}) &= e^{-\frac{F}{2\sigma^2}}, \\
 \mathrm{where } F &= \sqrt{\frac{\sum_{i=1}^n(s_i - m_i)}{n}}.
\end{aligned}
\end{equation}

$F$ represents the euclidean distance from a test fingerprint and a training fingerprint. $\sigma$ represents the measurement error from the test point, however the paper did not specify how it arrived at this value.

## Choosing the correct Value for the SD

We're not sure how to do this!

## MAP Estimate Results

```{r, echo=FALSE, fig.cap="Probability heat map for the positions in the test data, X is the actual point, O is the MAP estimate.", message=FALSE, warning=FALSE, fig.height=6}
estimotes = train$address %>% unique()
radioMaps = data.frame()

for (estimote in estimotes) {
  radioMaps = rbind(radioMaps, generateRadioMap(estimote = estimote, data = train))
}

# predict
predictions = mapEstimate(radioMaps = radioMaps, testData = test)

# X is the actual point, O is the predicted one
plotMapEstimate(predictions = predictions)
```

## Trilateration

## K-NN

We can use the generated radio maps to perform K-NN.